%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%----------------------------------------------------------------------------------------
 
\documentclass{resume} % Use the custom resume.cls style 
\usepackage[dvipsnames]{xcolor}
\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{HUANG Tin Yeh (Heaven)} % Your name 
\address{Department of Industrial and Systems Engineering, Faculty of Engineering,}
\address{The Hong Kong Polytechnic University, Hong Kong SAR, China, 999077}
\address{+852 9449 8934 \\ +86 198 9655 5044 \\ https://tyhuang.hk}
\address{tin-yeh.huang@connect.polyu.hk \\ hty25@mails.tsinghua.edu.cn \\ huangtianye@mails.x-institute.edu.cn}

\definecolor{TsinghuaPurple}{cmyk}{0.58,0.90,0,0}
\renewenvironment{rSection}[1]{
\sectionskip
\textcolor{TsinghuaPurple}{\MakeUppercase{#1}}
\sectionlineskip
\hrule
\begin{list}{}{
%\setlength{\leftmargin}{1.5em}
\setlength{\leftmargin}{0em}
}
\item[]
}{
\end{list}
}

\begin{document}  

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf The Hong Kong Polytechnic University (PolyU)} \hfill {Hong Hum, Kowloon, Hong Kong SAR}\\
{\textbf{B.Eng. (Hons)} in Product Engineering with a Second Major IE} \hfill \textit{September 2025 - May 2028 (Expected)}\\
{\textbf{B.Eng. (Hons)} Scheme in Product and Industrial Engineering} \hfill \textit{September 2024 - August 2025}

{\bf Tsinghua University} \texttt{(Exchange)} \hfill {Beijing, China}\\
{\textbf {B.Eng.} in Creative Design and Intelligent Engineering} \hfill \textit{September 2025 - January 2026 (Scheduled)}

{\bf College of Professional and Continuing Education (CPCE), PolyU} \hfill {Yau Ma Tei, Kowloon, Hong Kong SAR}\\
{\textbf{Associate} in Statistics and Data Science} \hfill \textit{September 2023 - August 2024}
\end{rSection} 

\begin{rSection}{Research Study}
{\bf Tsinghua University Tsien Excellent in Engineering Programme (TEEP) \& X-Institute} \hfill {Beijing, China}\\
{\textbf{Jointed Training Research Scholar} (Scoial and Intelligent Innovation)} \hfill \textit{September 2024 - May 2028 (Expected)}\\
{Supervisor: Prof. Ming TANG}

{\bf Shenzhen Medical Academy of Research and Translation (SMART)} \hfill {Shenzhen, Guangdong, China}\\
{\textbf{Visiting Research Student} - Institute of Biomolecular Architecture and Biological Interactions (IBABI)} \hfill \textit{June 2025 - July 2025}\\
{Supervisor: Dr. Mingxu HU (PI), Dr. Qi ZHANG}
\end{rSection}  

\begin{rSection}{Exchange}
1) Summer School on Mathematical Biology, Institute of Natural Sciences and School of Mathematics, Shanghai Jiao Tong University \hfill \textit{August 2025}

2)	Semester Exchange (2025/2026 Semester 1), Tsinghua University	\hfill \textit{September 2025 - January 2026}

3)	Social Innovation Training, Tsinghua University \& X-Institute \& ByteDance Ltd. \& Accenture Co. Ltd.	 \hfill \textit{January 2025}

4)	AI Winter School 2025, Center for the Fundamental Physics of the Universe \& Brown University	 \hfill \textit{January 2025}

5)	2024 Ministry of Education of PPC Teacher and Student Exchange Plan - Human-machine \hfill \textit{December 2024}\\ Shared Control Intelligent Car  Project, Northeastern University \& The Hong Kong Polytechnic University

6)	X-Challenge 2024: Interdisciplinary Cutting-edge Disruptive Innovation, Tsinghua University \& X-Institute \hfill \textit{June 2024 -- July 2024}

7)	X-Idea 2023: X-Institute International Summer School, Tsinghua University \& X-Institute \hfill \textit{June 2023 -- July 2023}
\end{rSection}

%--------------------------------------------------------------------------------------
%   Research Publications 
%--------------------------------------------------------------------------------------
\begin{rSection}{Publications}        

1. {Wang, X.\textsuperscript{*}, \textbf{Huang, T. Y.}, Jiang, Z., \& Wang, Y. (2025). Bio-Cryptography: Dual deep learning framework for protein watermarking via geometric-chemical fingerprinting [\textbf{Poster}]. International Conference on Machine Learning (ICML) 2025 Workshop on NewInML. \\\texttt{https://icml.cc/virtual/2025/50442}} 

2. {Wang, Y.\textsuperscript{*}, Wang, J., \textbf{Huang, T. Y.}, Yang, J., Yang, G., \& Xu, Z. (2025). STGCN-LSTM for olympic medal prediction: Dynamic power modeling and causal policy optimization [\textbf{Paper}]. International Conference on Machine Learning (ICML) 2025 Workshop on NewInML. \\
\texttt{https://doi.org/10.48550/arXiv.2501.17711}} 

3. {Wang, Y.\textsuperscript{*}, Cai, M., \& \textbf{Huang, T. Y.} (2025). AI for disease prediction: Performance insights and key limitations. \textit{Journal of Clinical Neuroscience, 138}, 111360. \texttt{https://doi.org/10.1016/j.jocn.2025.111360}} 

4. {Wang, X.\textsuperscript{*}, Wang, Y.\textsuperscript{+}, \& \textbf{Huang, T. Y.\textsuperscript{+}} (2025). Crypto-ncRNA: Encryption algorithm based on non-coding RNA (ncRNA) [\textbf{Poster}]. International Conference on Learning Representations (ICLR) 2025 Workshop on AI for Nucleic Acids (NA). \texttt{https://openreview.net/forum?id=j6ODUDw4vN}} 

\textit{\footnotesize \textsuperscript{*}\,First Author \quad \textsuperscript{+}\,Co-First Author}
\end{rSection}

%--------------------------------------------------------------------------------------
%   Academic Participaction 
%--------------------------------------------------------------------------------------
\begin{rSection}{ACADEMIC PARTICIPACTION}\itemsep -3pt

{\bf Reviewer} \quad \textit{\textbf{ICML 2025 Workshop} · 2nd AI for MATH} \hfill \textit{2025}

{\bf Reviewer} \quad \textit{\textbf{F1000 Research}} \hfill \textit{2025}
\end{rSection}

%-------------------------------------------------------------------------------
%	WORK EXPERIENCE
%-------------------------------------------------------------------------------

\begin{rSection}{WORK EXPERIENCE}
    {\bf AI Agent R\&D Parttime} \hfill \textit{March 2025 -- Present} \\ 
    \itab{Apricot AI Ltd.}

    {\bf Assistant to the President (Management \& Technical Director)} \hfill \textit{February 2025 -- Present} \\ 
    \itab{Hong Kong MBA Institute}

    {\bf AI Product \& Algorithm R\&D Intern} \hfill \textit{February 2025 --  Present} \\ 
    \itab{Qingbei Intelligent Technology Co., Ltd.}

    {\bf Student Intern} \hfill \textit{November 2024 -- December 2024} \\ 
    \itab{Research Centre - Data Science and Artificial Intelligence (RC-DSAI), PolyU}

    {\bf Student Assistant} \hfill \textit{October 2024 -- October 2025 (Expected)} \\
    \itab{Knowledge Transfer and Entrepreneurship Office, PolyU}

    {\bf Student Assistant} \hfill \textit{March 2023 -- May 2023} \\ 
    \itab{Division of Science, Engineering \& Health Studies, CPCE, PolyU}

    {\bf AI \& Data Trainee} \hfill \textit{December 2023 -- April 2024} \\ 
    \itab{Royal Plaza Hotel (Accounting \& IT Dept.)}\\
    
\end{rSection}

%-------------------------------------------------------------------------------
%	VOLUNTEERING
%-------------------------------------------------------------------------------

\begin{rSection}{Volunteering}
    {\bf Member, District Youth Development and Civic Education Committee} \hfill \textit{April 2025 -- April 2027 (Expected)} \\ 
    \itab{Home Affairs Department (HAD), The Government of the Hong Kong Special Administrative Region (HKGOV)} 

    {\bf Master of Ceremonies – 75\textsuperscript{th} PRC National Day Luncheon} \hfill \textit{October 2024}\\
    \itab{Hong Kong Federation of Trade Unions (HKFTU)} 

    {\bf Student Representative of B.Eng. (Hons) Product and Industrial Engineering (45498-PIE)} \hfill \textit{September 2024 – Now}\\
    \itab{Department of Industrial and Systems Engineering (ISE), PolyU} 

    {\bf Student Ambassador (Social Service Hours $>$ 30 Hours)} \hfill \textit{October 2023 -- October 2024} \\ 
    \itab{CPCE, PolyU}

    {\bf Student Representative of Associate in Statistics and Data Science (8C112-SDS)} \hfill \textit{September 2023 – August 2024}\\
    \itab{Division of Science, Engineering, and Health Studies (SEHS), CPCE, PolyU}
\end{rSection}

%-------------------------------------------------------------------------------
%	PROJECTS
%--------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\begin{rSubsection}{Multimodal BERT Model Based Global Heatwave Disaster Adaptation Elements Extraction \\and Analysis} {November 2024 - September 2025}{2024 Chinese Academy of Sciences (CAS) Undergraduate Innovation Practice Training Program}{}

\item This research uses a multimodal BERT model to integrate text, images, and structured data to precisely identify key factors affecting heatwave adaptation. The research results will provide solid theoretical and data support for formulating scientific global heatwave response strategies and enhance society's overall disaster adaptation capabilities.
\item Supervisor: Researcher Yong Ge (Institute of Geographic Sciences and Natural Resources Research, CAS, Distinguished Young Scholar)    
 
\end{rSubsection}  

%------------------------------------------------

\begin{rSubsection}{Research on Elderly Companionship Issues Based on AI Digital Twin Technology}{\textit{Dec 2024 - Dec 2025}}{Tsinghua University TEEP Enhanced Student Research Training (ESRT) Project}{} 
\item This project centers on AI digital twin technology, aiming to alleviate the lack of emotional companionship for elderly people in the context of China's aging population, while bridging the digital divide for seniors and enhancing AI practical capabilities for primary and secondary school students. The project is implemented jointly by Shenzhen X-Institute and ByteDance, among other institutions, divided into preparation, execution, and promotion phases. It plans to enhance intergenerational communication through students creating personalized digital twins for elderly people, exploring application scenarios of AI large models in social welfare fields.            
\item Min Tang (Former Counselor of the State Council)   
\end{rSubsection}

\end{rSection}

%---------------------------------------------------------------------------------
%  Achievements
%--------------------------------------------------------------------------------

\begin{rSection}{Achievements}
{\textbf{Scholarship} - HKSAR Government Scholarship Fund -- Reaching Out Award (ROA)} \hfill \textit{2025}

{\textbf{Scholarship} - PolyU ISE Sponsorship (International Conference)} \hfill \textit{2025}

{\textbf{Scholarship} - PolyU Undergraduate Entry Scholarship} \hfill \textit{2024}

{\textbf{Scholarship} - Overseas Exchange Scholarship (CPCE, PolyU)} \hfill \textit{2024}

{\textbf{Awards} - Most Academican Award (X-Institute)} \hfill \textit{2023}

{\textbf{Certification} - Microsoft Certified: Azure AI Fundamentals} \hfill \textit{2021}

{\textbf{Certification} - Advanced Level Certificate in Mathematics Enrichment Programme (PolyU)} \hfill \textit{2021}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{skills and INTERESTS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Computer-based  & Python (Pandas, PyTorch, TensorFlow, etc.), C++, SQL, SAS, R, CAD\&CAE (SolidWorks), Adobe (Photoshop, Illustrator,\\
                & InDesign), IMOD, PyMol, ChimeraX, LaTeX, MS Office\\
\\
Manufacturing   & Additive Manufacturing(FDM, SLA, SLS, etc.), Reverse Engineering, Quality Engineering, Robotics (Arduino/Raspberry Pi),\\ 
                &  Benchwork, Engineering Drawing\\
\\
Business        & Engineering Economics, Management and Organization, Marketing, Market Analysis, Engineering Law\\
\\
Soft skills     & Product \& Industrial Design, Product Development, Project Management, Design Thinking, Design for Many(Optimizing,\\ 
                & Manufacturing, Sustainability, etc.), Human-centered Design\\
\\
Languages       & Cantonese/Mandarin (Native), English (Fluent)\\

\end{tabular}   

\end{rSection}


%---------------------------------------------------------------------------------
%  DECLARATION
%--------------------------------------------------------------------------------

\begin{rSection}{ Declaration  } \itemsep -3pt        

\item I hereby declare that all the details furnished above are true to the best of my knowledge and belief.   
  
\end{rSection}
\end{document}
